CITK - an architecture and examples of CUDA enabled ITK filters

### 2011-05-20 trunk/article/Article.tex
minor extras in article - sending to other authors

\section{Installation and building}
\subsection{CUDA compiler and software development kit}
This framework requires CUDA 3.2 and the SDK. The {\em thrust} library
is also included in the examples to implement more complex components
of some sample filters.
\subsection{Patch ITK 3.20}
The code distributed with this article includes a patch to modify ITK
3.20, called {\em patch.3.20.0.dif}. This can be applied as follows:

\begin{itemize}
\item fetch \url{http://voxel.dl.sourceforge.net/sourceforge/itk/InsightToolkit-3.20.0.tar.gz}
\item extract
\item cd ITK-3.20
\item patch -p0 $<$ path/to/patch.3.20.0.dif
\end{itemize}

@@

\subsection{Build and install modified ITK}
There are many options available when building ITK. This process has
been tested under Linux and there are a number of changes to defaults
required to avoid limitations to the CUDA development tools. 
\begin{itemize}
  \item Specify location of CUDA SDK.
  \item Turn off SSE options for VNL - see advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
\end{itemize}

\subsection{Build examples}
The examples and tests are included in this package. The most up to
date version of the package can be found at \url{http://code.google.com/p/cuda-insight-toolkit/}.

>>>>

\section{Installation and building}
\subsection{CUDA compiler and software development kit}
This framework requires CUDA 3.2 and the SDK. The {\em thrust} library
is also included in the examples to implement more complex components
of some sample filters.
\subsection{Fetch this contribution from google code}
The source code is included with this article and is also available from google code:
\url{http://code.google.com/p/cuda-insight-toolkit/}. The patch for ITK is included.

\subsection{Patch ITK 3.20}
The code distributed with this article includes a patch to modify ITK
3.20, called {\em patch.3.20.0.dif}. This can be applied as follows:

\begin{itemize}
\item fetch \url{http://voxel.dl.sourceforge.net/sourceforge/itk/InsightToolkit-3.20.0.tar.gz}
\item extract
\item cd ITK-3.20
\item patch -p0 $<$ path/to/cuda-insight-toolkit/patch.3.20.0.dif
\end{itemize}

@@

\subsection{Build and install modified ITK}
There are many options available when building ITK. This process has
been tested under Linux and there are a number of changes to defaults
required to avoid limitations to the CUDA development tools. 
\begin{itemize}
  \item Specify location of CUDA SDK. Note that if there is trouble locating libcutil.a, it may be set explicitly under advanced options - CUDA\_CUT\_LIBRARY.
  \item Turn off SSE options for VNL - see advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
  \item Enable ITK\_USE\_REVIEW under advanced options, in order to build all of the tests.
\end{itemize}

\subsection{Build examples}
The Examples subdirectory in the citk distribution includes a
CMakeFile for building all examples and running tests. Location of the
patched ITK, nvcc and CUDA SDK must be provided during configuration.
